Incentivizing Optimal Forecasting Groups in Prediction Markets

### 2017-04-26 optimal_forecasts/Final Paper/article_2.tex
Now working on checking performance over random inclusion

\begin{equation}
\label{strictutil1}
\pi(\vec{p}, \theta) = G(\vec{p}) + C[GE(A,B) - GE(A+1,B)] \ if \ \theta=a
\end{equation}\\

\begin{equation}
\label{strictutil2}
\pi(\vec{p}, \theta) = G(\vec{p}) + C[GE(A,B) - GE(A,B+1)] \ if \ \theta=b
\end{equation}\\

@@

\resizebox{0.48 \textwidth}{!}{
$
C = \min\{{\frac{1}{|GE(A,B) - GE(A+1,B)|}, \frac{1}{|GE(A,B) - GE(A,B+1)|}}\}
$
}\\

@@

\resizebox{0.25 \textwidth}{!}{
$
C = \frac{1}{|GE(A,B) - GE(A,B+1)|}
$
}\\

@@

\resizebox{0.25 \textwidth}{!}{
$
C = \frac{1}{|GE(A,B) - GE(A+1,B)|}
$
}\\

\textit{Case 4}: $GE(A,B) - GE(A+1,B)>0$, $GE(A,B) - GE(A,B+1)>0$\\

@@

The two most salient issues with the strict incentive scheme above is the reliance on severe incentives to exclude a particular type and a lack of liquidity as the size of the participating pool increases. We would like to propose a way to relax these incentives while knowing the types of the individuals that are included in the participating pool. If the incentives for both types are greater than -1, that leaves the possibility that both types could participate. Therefore, the market organizer will need to elicit the types from the agents themselves, and the incentive scheme must guarantee that it is always in the best interests of each agent to report their type truthfully.

Previously, the scheme made the payoff for any market participant proportional to the accuracy and sharpness of their prediction as well as their effect on the expected accuracy of the group prediction.

>>>>

\begin{equation}
\label{strictutil1}
\pi(\vec{p}, \theta) = G(\vec{p}) + C[GE(A,B) - GE(A+1,B)] \ if \ \theta=a
\end{equation}

\begin{equation}
\label{strictutil2}
\pi(\vec{p}, \theta) = G(\vec{p}) + C[GE(A,B) - GE(A,B+1)] \ if \ \theta=b
\end{equation}

@@

\resizebox{0.48 \textwidth}{!}{
$
C = \min\{{\frac{1}{|GE(A,B) - GE(A+1,B)|}, \frac{1}{|GE(A,B) - GE(A,B+1)|}}\}
$
}\\
\newline

@@

\resizebox{0.25 \textwidth}{!}{
$
C = \frac{1}{|GE(A,B) - GE(A,B+1)|}
$
}\\
\newline

@@

\resizebox{0.25 \textwidth}{!}{
$
C = \frac{1}{|GE(A,B) - GE(A+1,B)|}
$
}\\
\newline
\textit{Case 4}: $GE(A,B) - GE(A+1,B)>0$, $GE(A,B) - GE(A,B+1)>0$\\

@@

The two most salient issues with the strict incentive scheme above is the reliance on severe incentives to exclude a particular type and a lack of liquidity as the size of the participating pool increases. We would like to propose a way to relax these incentives while knowing the types of the individuals that are included in the participating pool. If the incentives for both types are greater than -1, that leaves the possibility that both types could participate. Therefore, the market organizer will need to elicit the types from the agents themselves, and the incentive scheme must guarantee that it is always in the best interests of each agent to report their type truthfully.\\

Previously, the scheme made the payoff for any market participant proportional to the accuracy and sharpness of their prediction as well as their effect on the expected accuracy of the group prediction. Had the individuals been asked to self-report types, there would be no incentive to either lie or tell the truth, since the incentives are not linked to their reported type but to their actual type. To ensure that there is a strict incentive to tell the truth, we propose the following addition to the scheme from earlier.
\newline

\resizebox{0.45 \textwidth}{!}{
$
\pi_i(\vec{p}, \theta) = G(\vec{p}) + C[GE(A,B) - GE(A+1,B)] - \sum_{j>i} e^{-j} \Delta GE_j \ if \ \theta=a
$
}\\

\resizebox{0.45 \textwidth}{!}{
$
\pi_i(\vec{p}, \theta) = G(\vec{p}) + C[GE(A,B) - GE(A,B+1)] -  \sum_{j>i} e^{-j} \Delta GE_j\ if \ \theta=b
$
}\\
\newline

where $j$ indicates an agent that participates after the current agent $i$ participates. Furthermore, $\Delta GE_j$ is short for the change in expected group error following the inclusion of $j$. If $\Delta GE_j > 0$, expected group error increased, hence the subtraction of this term from the expected payoff.\\

This term will reward current participants in the market if future participants bring the expected group error down as well. This term provides agent $i$ with a positive incentive to report their type truthfully. If the agent reports untruthfully, it does not affect that agent in the near term but it will skew the known proportions in the crowd such that future agents cannot make fully-informed decisions as to whether or not they are of the right type for the market at that moment. This could lead to the inclusion of the wrong type at a particular stage in the market after $i$ has participated.
